dendro

### 2017-04-10 analysis/test-bai.Rmd
update bai

>>>>

```{r}
set.seed(1234)
serie <- sample(colnames(b_test_dplR),1)

require(reshape2)

bp <- melt(t(b_test_piovesan))
names(bp) <- c('cores', 'years', 'bai_p')

bd <- melt(t(b_test_dplR))
names(bd) <- c('cores', 'years', 'bai_d')

diff <- bp %>% 
  inner_join(bd, by=c('cores','years')) %>% 
  mutate(diff = bai_p - bai_d)

ggplot(x, aes(y=bai, x=years, colour=test)) + 
  geom_point() + 
  facet_wrap(~cores)
